### 2012-03-11 intention motor representation with corrado sinigaglia/intention and motor action.tex
cambridge added

While there are good reasons to resist both temptations (or so we shall argue), the recognition that motor representation can ground the outcome-directedness of purposive actions independently of intention gives rise to a problem. For a single action, which outcomes it is directed to may be multiply determined by an intention and, seemingly independently, by a motor representation. Unless such intentions and motor representations are to pull an agent in incompatible directions, which would typically impair action execution, there are requirements concerning how the outcomes they represent must be related to each other. The problem is to explain how any such requirements could be met non-accidentally; we call this `the interface problem' . The key to solving this problem, we shall suggest, is to recognise that intentions can have constituents which refer to outcomes by deferring to motor representations of those outcomes. Effective action sometimes requires that the contents of intentions and of motor representations interlock, and this interlocking occurs when the contents of intentions are determined in part by the contents of motor representations.  So whereas discussions of intention frequently ignore motor aspects of action, it turns out that understanding how intentions interface with motor representations is required for fully understanding how intentions are related to actions.

@@

So far we have been arguing that motor and visual representations differ in format.  Why suppose that motor representations also differ in format from intentions?  As we noted earlier, the format of a representation constrains its possible contents. Just as a representation's having a cartographic format restricts its possible contents, so the motor format would imply restrictions on representations having it. In imagining executing actions such as grasping a cup, there are bio-mechanical, dynamical and postural constraints, among others, on what can be imagined. These constraints are closely related to those which govern actually performing such actions \citep{Jeannerod:2001yb} . Such constraints are plausibly explained by the representational format of motor representations. Since no such constraints would be expected to apply where propositional representations are involved, we can conclude (as is widely assumed) that the format of motor representations is not propositional.

>>>>

While there are good reasons to resist both temptations (or so we shall argue), the recognition that motor representation can ground the outcome-directedness of purposive actions independently of intention gives rise to a problem. For a single action, which outcomes it is directed to may be multiply determined by an intention and, seemingly independently, by a motor representation. Unless such intentions and motor representations are to pull an agent in incompatible directions, which would typically impair action execution, there are requirements concerning how the outcomes they represent must be related to each other. The problem is to explain how any such requirements could be met non-accidentally; we call this `the interface problem'. The key to solving this problem, we shall suggest, is to recognise that intentions can have constituents which refer to outcomes by deferring to motor representations of those outcomes. Effective action sometimes requires that the contents of intentions and of motor representations interlock, and this interlocking occurs when the contents of intentions are determined in part by the contents of motor representations.  So whereas discussions of intention frequently ignore motor aspects of action, it turns out that understanding how intentions interface with motor representations is required for fully understanding how intentions are related to actions.

@@

So far we have been arguing that motor and visual representations differ in format.  Why suppose that motor representations also differ in format from intentions?  As we noted earlier, the format of a representation constrains its possible contents. Just as a representation's having a cartographic format restricts its possible contents, so the motor format would imply restrictions on representations having it. In imagining executing actions such as grasping a cup, there are bio-mechanical, dynamical and postural constraints, among others, on what can be imagined. These constraints are closely related to those which govern actually performing such actions \citep{Jeannerod:2001yb}. Such constraints are plausibly explained by the representational format of motor representations. Since no such constraints would be expected to apply where propositional representations are involved, we can conclude (as is widely assumed) that the format of motor representations is not propositional.
